\bf Faster Neural Machine Translation Inference

### 2018-02-22 fast-beam/fast-beam.tex
fast

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		& Baseline	& Fused \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 1}}	\\ \hline	
Multiplication 	& 21.47 	& 21.94 (+2.2\%) \\ \hline
Add bias 	& 33.59		&  \\ 
Softmax 	& 8.83		& 5.70 (-89.9\%)\\
Beam search	& 13.91		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 5}}	\\ \hline	
Multiplication 	& 79.66 	& 80.01 (+4.4\%) \\ \hline
Add bias 	& 14.95		&  \\ 
Softmax 	& 36.86		& 42.91 (-64.4\%)\\
Beam search	& 68.80		&  \\ \hline
\end{tabular}
\end{center}
\caption{Time taken in sec (OpenSubtitles)}
\label{tab:fused-breakdown-opensubtitles}
\end{table}

>>>>

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		& Baseline	& Fused \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 1}}	\\ \hline	
Multiplication 	& 21.47 	& 21.94 (+2.2\%) \\ \hline
Add bias 	& 3.29		&  \\ 
Softmax 	& 8.83		& 5.70 (-78.1\%)\\
Beam search	& 13.91		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 5}}	\\ \hline	
Multiplication 	& 79.66 	& 80.01 (+4.4\%) \\ \hline
Add bias 	& 14.95		&  \\ 
Softmax 	& 36.86		& 42.91 (-64.4\%)\\
Beam search	& 68.80		&  \\ \hline
\end{tabular}
\end{center}
\caption{Time taken in sec (OpenSubtitles)}
\label{tab:fused-breakdown-opensubtitles}
\end{table}
